Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey

### 2022-12-14 docs/manuscript/manuscript.tex

A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis. The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards. The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}

\subsection{Survey Demographics}

\subsection{Definition of Reproducibility}
Definition Questions and Q8 about beliefs about the interpretation for reproductions. Dig into those respondents that had variations in beliefs on Q8 sequence. Q17 about importance of reproduction. Close with Q13.

\subsection{Familiarity and Frequency of Practices}
Summary of Table showing Familiarity 1) all survey, 2) Methods, 3) Subfield Split
Summary of Table showing Implementation 1) all survey, 2) Methods, 3) Subfield Split

\subsection{Actual Reproductions}
Summary of Q10-Q12

\subsection{Barriers to Reproduction}
Q14

>>>>

\subsection*{Survey Demographics}
A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis. The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards. The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.} 
ADD COMPARISON TO SAMPLE FRAME.

\subsection*{PCAish Summary Across Dimensions}
This subsection will pivot on Table 9 that has rows representing PCA-like aggregate measures of 1) definition, 2) Familiarity 3)practice, 4) Barriers and two groups of rows (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).

\subsubsection*{Definition of Reproducibility}
Definition Questions and Q8 about beliefs about the interpretation for reproductions. Dig into those respondents that had variations in beliefs on Q8 sequence. Q17 about importance of reproduction. Close with Q13.

\subsubsection*{Familiarity with Reproduciblity Practices}

\subsubsection*{Frequency of Reproduciblity Practices}

Q9 will feather in to contextualize the measure

\subsubsection*{Barriers to Reproduction}
Discussion of details from Q14

\subsection{Actual Reproductions}
Start with the outline of what the population is here because not all respondents answered these questions. Start with descriptives that show this sub-sample of respondents. Summary discussion of Q10-Q12.
